Examining Crowd Work and Gig Work Through The Historical Lens of Piecework

### 2017-05-03 chi/piecework/presentation/complexity.tex
complexity stuff

\begin{frame}{Humble origins}
  First implementations of piecework:
  \visible<2->{farms}\visible<3->{, textiles}\visible<4->{, and other low--skill labor.}
  \begin{columns}

  \visible<2->{
  \begin{column}{0.3\textwidth}
  \begin{figure}
  \includegraphics[width=\textwidth]{figures/idk.png}
  \end{figure}
  \end{column}
  }

  \visible<3->{
  \begin{column}{0.3\textwidth}
  \begin{figure}
  \includegraphics[width=\textwidth]{figures/pieceworkers.jpg}
  \end{figure}
  \end{column}
  }

  \visible<4->{
  \begin{column}{0.3\textwidth}
  \begin{figure}
  \includegraphics[width=\textwidth]{figures/photo/Matchgirl_strikers.PNG}
  \end{figure}
  \end{column}
  }
  \end{columns}
\end{frame}

\begin{frame}{Ford}
    Fordism

>>>>

\begin{frame}{Cottage Industry}
  First appearances of piecework:
\visible<2->{farms}%
\visible<3->{, textiles}%
\visible<4->{, and matchsticks.}
  \begin{columns}

  \visible<2->{
  \begin{column}{0.33\textwidth}
  \begin{figure}
  \includegraphics[width=\textwidth]{figures/idk.png}
  \end{figure}
  \end{column}
  }

  \visible<3->{
  \begin{column}{0.33\textwidth}
  \begin{figure}
  \includegraphics[width=\textwidth]{figures/pieceworkers.jpg}
  \end{figure}
  \end{column}
  }

  \visible<4->{
  \begin{column}{0.33\textwidth}
  \begin{figure}
  \includegraphics[width=\textwidth]{figures/photo/Matchgirl_strikers.PNG}
  \end{figure}
  \end{column}
  }
  \end{columns}
\end{frame}

\begin{frame}\frametitle{Planes, trains, and automobiles}
             \framesubtitle{{\dots~not in that order}}

  \begin{columns}
  % \vspace{1mm}
  \only<1,4->{
  \begin{column}{0.33\textwidth}
  \centering
  Trains
  \begin{figure}
    \begin{overlayarea}{\textwidth}{4cm}
    \begin{minipage}[c][4cm]{\textwidth}
      \includegraphics[width=\textwidth]{figures/photo/train-engineer.jpg}
    \end{minipage}
    \end{overlayarea}
    % \caption{i wanna fly the train}
    \end{figure}
\end{column}

\only<1>{
    \begin{column}{0.66\textwidth}
      \begin{itemize}
        \item Train engineers were among the first skilled workers to experience piece--rate payment systems
        \item ``Efficiency experts'' occasionally came by to evaluate how long it took to do various jobs
        \item This led to slow--walking the job, to offset the fact that
              efficiency experts weren't accounting for liminal work.
      \end{itemize}
    \end{column}
  }
}

  \only<2,4->{
    \only<2>{
      \begin{column}{0.33\textwidth}
      \begin{itemize}
        \item Ford, Taylor, and others moved quickly
              monitor and measure professionals.
      \end{itemize}
      \end{column}
    }

  \begin{column}{0.33\textwidth}
    \centering
      Automobiles
      \begin{figure}
        \begin{overlayarea}{\textwidth}{4cm}
        \begin{minipage}[c][4cm]{\textwidth}
          \includegraphics[width=\textwidth]{figures/idk.png}
        \end{minipage}
        \end{overlayarea}
        % \caption{something something}
      \end{figure}
  \end{column}

  \only<2>{
    \begin{column}{0.33\textwidth}
    \begin{itemize}
      \item \textit{Manufacturing} proved amenable
            to assembly line processes.
    \end{itemize}
    \end{column}
  }
}

  \only<3->{
    \only<3>{
      \begin{column}{0.66\textwidth}
      \end{column}
    }
  \begin{column}{0.33\textwidth}
    \centering
      Planes
      \begin{figure}
        \begin{overlayarea}{\textwidth}{4cm}
        \begin{minipage}[c][4cm]{\textwidth}
            \includegraphics[width=\textwidth]{figures/photo/Rosie_the_Riveter_(Vultee)_DS.jpg}
      \end{minipage}
      \end{overlayarea}
      % \caption{i wanna fly the plane}
      \end{figure}
  \end{column}
  }

  \end{columns}

\begin{frame}{Ford}
    % Fordism
